A model-based method for detecting persistent cultural change using panel data[^thanks]

### 2021-01-28 ms.Rmd
typo fixes

---
title: A model-based method for detecting persistent cultural change using panel data[^thanks]
author:
  - Stephen Vaisey[^SV]
  - Kevin Kiley[^KK]
date: "12/16/2020"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
# header-includes:
#   - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 11pt
---

@@

From this basic version, we can add further constraints. For example we can constrain $\alpha_1 = \alpha_2 = \alpha_3$ if we are willing to assume that the mean response is the same at all waves. And we could constrain $\sigma^2_{\epsilon_1} = \sigma^2_{\epsilon_2} = \sigma^2_{\epsilon_2}$ if we are willing to assume that the variance of the responses does not change over time.

@@

These findings have clear implications for cultural sociology and public opinion research, favoring models of cultural change rooted in cohort replacement [@mannheim1952; @ryder1965] and those that place importance on early-life socialization over contemporary social environments [such as @bourdieu1990]. We believe that these findings are also relevant for research on cultural evolution [see @henrich2015; @heyes2018; @mesoudi2016] because they place significant limits on the likely pace and mechanisms of cultural change. Cohort-based change will necessarily be slower than that implied by simple population models of social learning. This lag process allows cultural equilibria to be durable even when the contemporary information environment is changing [@oconnor2019]. We hope future research explores these links more directly.

>>>>

---
title: A model-based method for detecting persistent cultural change using panel data[^thanks]
author:
  - Stephen Vaisey[^SV]
  - Kevin Kiley[^KK]
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
# header-includes:
#   - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 11pt
---

@@

From this basic version, we can add further constraints. For example we can constrain $\alpha_1 = \alpha_2 = \alpha_3$ if we are willing to assume that the mean response is the same at all waves. And we could constrain $\sigma^2_{\epsilon_1} = \sigma^2_{\epsilon_2} = \sigma^2_{\epsilon_3}$ if we are willing to assume that the variance of the responses does not change over time.

@@

These findings have clear implications for cultural sociology and public opinion research, favoring models of cultural change rooted in cohort replacement [@mannheim1970; @ryder1965] and those that place importance on early-life socialization over contemporary social environments [such as @bourdieu1990]. We believe that these findings are also relevant for research on cultural evolution [see @henrich2015; @heyes2018; @mesoudi2016] because they place significant limits on the likely pace and mechanisms of cultural change. Cohort-based change will necessarily be slower than that implied by simple population models of social learning. This lag process allows cultural equilibria to be durable even when the contemporary information environment is changing [@oconnor2019]. We hope future research explores these links more directly.

### 2021-01-28 ms_anonymized.Rmd
typo fixes

---
title: A model-based method for detecting persistent cultural change using panel data[^thanks]
date: "12/19/2020"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
header-includes:
  - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 12pt
---

>>>>

---
title: A model-based method for detecting persistent cultural change using panel data[^thanks]
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
header-includes:
  - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 12pt
---
